\subsubsection{12.02.15 (Competition)}
\begin{center}
	2-nd day of competition "Robofest-2015"
\end{center}
Today there were qualification matches. \newline

After qualification marches we conducted technical inspection of our robot and twirled all screws. The construction of robot wasn't changed.\newline

First organizators planned to spend 40 matches (every team plays 5 matches) but due to problems with field control system they spent only 32 matches (4 for every team) \newline
 
Results of matches: 3 wins from 4.\newline

Matches where we won finished with good score. In every matches we got an average of 50 points for autonomous (robot did 2 or 3 actions from 4). It talk about low accuracy of moving by encoders. In tele op we captured 90cm goal and put into it 8 - 10 big balls (about 60cm - 180 points) then release it in the parking zone (10 points) and put 2 - 3 big balls to the center goal (about 90 - 140 points). That is we followed a planned strategy. \newline

In the second game we got a big count of points - 495. We made it because we reach effective teamplay with our ally (team "Sirius" from Ryazan). Our teammate had low accuracy of throwing balls into rolling goals. So we rised our lift, overturned the bucket and they put their balls on our gutter and balls got into rolling goal. So we filled the 90cm goal then we put 3 big balls into center goal and went to parking zone. Our ally went to the ramp and moved one rolling goal to it.\newline

We lost third game because we forgot to put autonomous balls and didn't get points for them. In addition our robot for unknown reasons didn't turn to the parking zone and knock the stick of opponents. Also we made a lot of mistakes in tele op period and filled 90cm goal on only 30cm and didn't put the balls into center goal.\newline

Format of protection engineering book changed. Now judges went to us during the brake between qualification matches. The plus of this format is that we can to demonstrate at the field opportunities of our robot. We talked with judges well. Results are unknown.\newline

Main problems identified during matches:
\begin{enumerate}
	\item Our gripper was narrow. So we had problems with capturing balls. 
	
	\item Some team blocked way to rolling goal during autnomous period. So it impossible to put autonomous balls into rolling goals and move rolling goals to the parking zone. We didn't play with team with this strategy but we understood vulnerability of our autonom.
	
	\item Before the last match it found that our MOB can't overturn bucket with five balls. This was because servo partically spoiled. We didn't have new powerful servo so we should to capture only 4 balls.
	
\end{enumerate} 

\fillpage