\section{Engineering section}
\subsection{Concept of robot}
\subsubsection{Construction}
\begin{itemize}
	\item Robot should be mobile, move quickly, and if it is possible in each of four direction.
	\item Robot should own four sensors of angle (encoder) to use it in the autonomous period.
	\item Robot should be compact and doesn't fill too much space, because it shouldn't hinder to ally.
	\item Robot must be able to monitor the five (5) goals simultaneously. 
	\item The robot must own special device for moving the movable baskets.
	\item If possible, the robot should be light, because it will be easier to carry.
	\item Construction of robot should let us to change some elements quickly.
\end{itemize}
\subsubsection{Autonomous period}
\begin{itemize}
	\item Robot should own some different versions of the autonomous period and use it, depending on possibilities of the ally, place of starting and others conditions.
	\item The program is an autonomous period should be simple.
\end{itemize}
\subsubsection{Driver-controlled period}
\begin{itemize}
	\item Controlling of the robot should be simple and convenient
	\item One operator is fully responsible for the movement of our robot, second - for all another functions.
	\item Some steps in the controlled period may be  implemented independently, to help operator.
	\item Operator should control speed of robot, because robot should perform precise manipulation.
\end{itemize}
\fillpage

\subsection{Strategy} 
\subsubsection{Autonomous period}
\begin{enumerate}
    \item Put two autonomous balls in two different baskets.
	\item Take the maximum number of mobile baskets and replace them to the parking area.
	\item On the way to the parking area it should set in motion mechanism of release balls.
	         
\end{enumerate}
\subsubsection{Driver-controlled period - main part}
\begin{enumerate}
	\item Let to our ally free access to the moving baskets. But, at the same time, it should carry one basket, because we should save the time.
	\item First, fill balls 90-cm basket, then - 60-cm and 30-cm .
	\item Avoid collisions with ally and opponents, because of vaste time .
\end{enumerate}
\subsubsection{Driver-controlled period - final}
\begin{enumerate}
	\item Fill the central basket with balls.
	\item Replace maximum possible number of the mobile baskets on the ramp.
	\item Call the robot on the ramp. 
\end{enumerate}
\fillpage

\subsection{Planned steps for creating of robot}
\begin{enumerate}
	\item Creating a wheel (or track ) base of the robot.
	\item Writing a program for controlling the wheelbase throught one (1) joystick.
	\item Creating a system of control goals.
	\item Writing a programm for control robot through two(2) joysticks.
	\item Writing programm for the autonomous period.
	\item Creating additional decorative elements.
	\item Installation on the robot protection elements to prevent damage during an accidental collision.
	\item Trainings (alone or with another robots).
	\item Making improvements on the basis of first competition.
\end{enumerate}
\fillpage
