\subsubsection{28.02.15}

\begin{enumerate}
	\item Time of beginning and ending of meeting:
	16:00 - 22:00
	\item Purposes of meeting:
	\begin{enumerate}
		\item To make the new bucket.
		
		\item To fix the ramp.
	  
    \end{enumerate}
   
	\item Work that has been done:
	\begin{enumerate}
		 
		 \item The ramp was fixed to the slopes with help of 4 corners from the Tetrix set.
		 
		 \item Today we projected a new bucket. We took the old bucket and modeled various scenarios. We try to reduce the angle of the bucket. So the balls should roll slower and straight. But it was wrong: balls continued stuck in the bucket.
		 
		 \item Also we discussed different buckets complex form. For example bucket with zigzag tube. But it was decided to fefuse from this variants because this bucket has more places where balls can stuck.
		 
		 \item It was found that if we install the plates that will smooth corners of the bucket balls will pass throught the bucket without problems. But this bucket will take more the place because due to the plates 5 balls will not fit in the bucket with the dimensions of previous bucket. So it will need to reduce the length of the ramp.
		 
    \end{enumerate}
    
	\item Result: 
	\begin{enumerate}
	  \item The ramp was fixed.
	  
	  \item The new bucket was elaborated
      
    \end{enumerate}
    
	\item Tasks for the next meetings:
	\begin{enumerate}
		
		\item To make the new bucket.
		
		\item To reduce the length of the ramp.
	  
    \end{enumerate}     
\end{enumerate}
\fillpage