\subsubsection{06.10.14}

\begin{enumerate}
	\item The time of beginning and ending of the meeting:
	21:00 - 21:30
	\item Purposes of the meeting:
	\begin{enumerate}
		\item To begin writing a program to control the robot by joystick.
		
	\end{enumerate}
	\item Work that has been done:
	\begin{enumerate}
		\item Two programs were written to test the wheel base: moving in a straight line and turning around. It showed great results driving in a straight direction, not deviating from the original trajectory. During the turning around robot jitters due to the high coefficient of friction between the wheels and the floor. So the wheels could not slip on the floor and jumped up and down. In general it does not affect the accuracy of the turn. The robot rotates exactly around its center of mass, but the latter is located not in the center of the robot, but closer to its tail part. For ease of control, perhaps the center of mass could be shifted closer to the intersection of the diagonals of the square to which the wheels are attached. Then the space needed to turn would be smaller and we would not hinder allies. 
		
		\item  As a result of the discussion we made our choice of lift type - sliding rails the bases of which are rigidly fixed to the frame of the robot. This design is most reliable and the easiest to implement.
		
	\end{enumerate}
	
	\item Results: 
	\begin{enumerate}
		\item  Type of lift was choosen.
		
	\end{enumerate}
	
	\item Tasks for the next meetings:
	\begin{enumerate}
		\item To buy furniture slats to create lift.
		
	\end{enumerate}     
\end{enumerate}
\fillpage