\subsubsection{07.02.15}
\begin{enumerate}
	
	\item The time of beginning and ending of the meeting: 16:30 - 20:00.
	
	\item Purposes of the meeting:
	\begin{enumerate}
		
		\item To train on the throwing balls to 90cm goal. To reduse the time of filling it.
		
	\end{enumerate}

	\item Work that has been done:
	\begin{enumerate}
		
		\item Today we trained but the middle time of filling 90cm goal stayed 2.5min.
		
		\item It was discussed the strategy of tele op period. We decided that the best strategy is
			\begin{enumerate} 
				\item Capture 90cm goal (usually we do it in autonomous period).
				 
				\item Put the maximal count of balls to 90cm goal. 
				
				\item Move 90cm goal to the parking zone (it is more safely than move it to the ramp because we can to turn over it). 
				
				\item When there is left 45sec to end of the match start to collect balls for the center goal. Then ride to the center goal and wait for end game.
				
				\item Put the balls to the center goal when the end game starts.
				
				\item Ride to the ramp if 15sec or more lefts to end of the match. Else ride to the parking zone.
				
			\end{enumerate}
		
	\end{enumerate}
	
	\item Results:
	\begin{enumerate}
		
		\item It was elaborated the strategy of tele op period.
		
	\end{enumerate}
	
	\item Tasks for the next meetings:
	\begin{enumerate}
		
		\item To train on the control robot .
		
		\item To make programme of autonomous period from the ramp.
		
		\item To imrove the protection from the small balls and the stick.
			
	\end{enumerate}
\end{enumerate}
\fillpage
