\subsubsection{21.01.15}
\begin{enumerate}
	
	\item Time of beginning and ending of meeting: 18:10 - 20:40.
	
	\item Purposes of meeting: 
	\begin{enumerate}
		
		\item To write the programme of autonomuos period for start from the parking zone.
		
		\item To train on the control robot.
		
	\end{enumerate}

	\item Work that has been done:
	\begin{enumerate}
		
		\item Today operator that responsible for control lift and MCB wasn't on the meeting. So there weren't trainings.
		
		\item Strategy of autonomuos period for start from the parking zone is: ride to 30cm goal and put the ball into it (from the hook). Then turn and ride to 90cm goal and put the second autonomuos ball into it (from the bucket). Then move this goals to the parking zone ().
		
        \item It was decided to make an additional hook for the autonomous ball because the first hook is higher than the edge of 30cm goal. In addition it will need to install additional gripper for rolling goal because we will can't to push it (it will too complex to put this goal on the line that connects 90cm goal with the parking zone).
		
	\end{enumerate}
	
	\item Results:
	\begin{enumerate}
		
		\item Programme of autonomous period for start from the parking zone was wrote.
		
		\item There were no trainings.
		
	\end{enumerate}
	
	\item Tasks for the next meetings:
	\begin{enumerate}
		
		\item To train on the control robot.
		
		\item To make an additional hook for autonomuos ball and additional gripper for rolling goal.
			
	\end{enumerate}
\end{enumerate}
\fillpage
