
\subsubsection{17.10.14}

\begin{enumerate}
	\item The time of beginning and ending of the congregation:
	17:00 - 20:00
	\item Purposes of the congregation:
	\begin{enumerate}
	  \item Write a program to control the gripper and connect it to the robot control program.
	  
    \end{enumerate}
    
	\item Work, that has been done:
	\begin{enumerate}
	  \item Program of servo control was written. By pressing the drive is switched on, and after the operator removes his hand from the button, it stops. During the tests, it became clear that such system is inconvenient for the operator, because he needs to keep his hand on the button.At the moment, all commands are served from one joystick, but then the first operator will be have only traffic control duties, and everything else will make the operator №2.
      
      \item When tested on a test version of the gripper banks (balls we haven't at that time ) it turned out that he, instead of capturing them, repels them.We understood that ties are fixed to the axis of the actuator upside down and decided to rearrange them, but still did not do it.
      
      \item In addition, it was decided to relocate the front crossmember further from the axis so that it does not obstruct the movement of the brush-ties.
      
      \item Consolidate ties on the axis was decided by a hot-melt adhesive, but since this session it we had, we decided to postpone everything until tomorrow classes.
      
      \item It has been observed that the travel stops furniture racks can not withstand weight of lift and rail's moving parts fail. In this regard, the data needs to be strengthened without compromising mobility constraints furniture racks.
      
    \end{enumerate}
    
	\item Results: 
	\begin{enumerate}
	  \item A simple program to manage the capture has been written.
	  
      \item Gripper was tested in action. Developed ideas to improve it.
      
    \end{enumerate}
    
	\item Tasks for the next congregations:
	\begin{enumerate}
	  \item Create a final version of gripper.
	  
	  \item Change management program for the gripper of more convenient.
	  
	  \item Strengthen the travel stops furniture racks.

    \end{enumerate}     
\end{enumerate}
\fillpage
