\subsubsection{14.12.14 (Competition)}
\begin{center}
	2-nd day of competition "Robofest-Ryazan"
\end{center}
Today there were qualification and final matches and protection of engineering books.
\newline 

Main problems that were found during the matches:
\begin{enumerate}
	\item Wires that connect MOB with servocontroller often loses contact between themselves. So operator couldn't to control it.
	
	\item Wires that connects drivers of motors and battery were closed on each other. So battery started to hot.
	
	\item Bucket was cracked due to kicks on rigid obstacles (for example center goal).
	
	\item It was found that the lift shakes during the rising. So some balls fall outside the bucket.
	
	\item Sometimes balls stuck on the additional slopes because they wasn't closed from the top.
	
\end{enumerate}

Results:
\begin{enumerate}
	\item We didn't get to "top 2" by the results of qualification matches.
	
	\item We took part in the final match becauce team "PML 30 ${\psi}$" choosed us. Our alliance took first place.
	
	\item We took first place in nomination "Engineering book".
\end{enumerate}

Summing up:
\begin{enumerate}
  \item Succsess of performance on competition:
  \begin{enumerate}
	\item Our alliance took first place. It is mainly due to our teammate - "PML 30 ${\psi}$".
	
	\item We took first place in nomination "Engineering book".
	
  \end{enumerate}
  
  \item Our mistakes and disadvantages in construction:
  \begin{enumerate}
  	\item Wiring was not reliable. So we often had problems with MOB and motors.
  	
  \end{enumerate}
  
  \item Tasks for the next meetings:
  \begin{enumerate}
  	\item To replace wiring to more reliable.
  	
  	\item To make more comfortable programme of control robot's moving.
  	
  	\item To make bucket of quality plastic.
  	
  	\item To make additional slopes that will be closed from the top.
  	
  	\item It was found that it unprofitable to capture small balls. So we should to remove the screw that stops the blades.
  	
  	\item To make MCB that can to keep the rolling goal when robot is on the ramp after power off.
  	  	
  	\item To install slopes for alignment rolling goal.
  	
  	\item One motor that moves robot broke during the final match. It must be raplaced.
  	
  \end{enumerate}
  
\end{enumerate}
\fillpage